### 2007-01-11 Documentation/Manual.tex
*** empty log message ***

TO BE UPDATED [WW].

Here we briefly summarize the main changes of the new GLoBES version. For details, please
refer to the respective parts of the manual. Please note that any new \GLOBES\ version is
compatible with older versions, \ie, old application software and AEDL files should also run with the new version. EXCEPTION: VERSION NUMBER IN AEDL REQUIRES? [WW] However, some function names and features will
evolve during time, which means that outdated features may not be documented anymore.

@@

Here comes a summary of the most important changes in this version for older users of GLoBES.

@@

\begin{itemize}
 \item
  User-defined systematics to simulate experiments with correlated systematics \etc\ (such as
reactor experiments); see \Sec~?
 \item
  User-defined priors to include arbitrary external information in the $\chi^2$ before
marginalization over the oscillation parameters (such as to prevent minimizer from
running into the wrong octant \etc); see \Sec~?
\item
  Non-standard physics support; see \Sec~?
\item
  Beta beam fluxes available as built-in fluxes; see \Sec~?
\item
  Enhanced support for parallelization, such as Condor; see \Sec~?
\item
  Updated AEDL files, new beta beam files; see \Sec~?
\item
 Faster probability engine
\item
  ...
\end{itemize}

@@

Most of the modifications below should not require that old pieces of software be changed. 
However, the following changes are necessary:
\begin{itemize}
\item
 AEDL requires now that {\tt \$version} be used to define the minimum version number this AEDL
file is to be used with. With this requirement one can easily avoid that new AEDL
files with new features be used with old versions of \GLOBES\ which may not recognize these features.
\item
 Some of the earlier AEDL files have been updated, changed names, or have been removed. In addition, new files have been added. Although old AEDL files will run as usual for compatibility, they will not be
supported by the \GLOBES\ team anymore. You should make sure to keep these files when updating \GLOBES . 
\item
 ...
\end{itemize}
The following changes should not affect older software:
\begin{itemize}
\item
 {\tt glbChi...} functions renamend for consistency
\item
 {\tt glbChiSetStartingValues} and {\tt glbChiGetStartingValues} renamed into 
{\tt glbChiSetCentralValues} and {\tt glbChiGetCentralValues}
\item
 Systematics concept changed, concept of error dimensions removed
\item
 Some functions changed (such as for direct rate access)
\item
 ..
\end{itemize}

>>>>

Here we briefly summarize the main changes of the new GLoBES version. For details, please
refer to the respective parts of the manual. Please note that any new \GLOBES\ version is
compatible with older versions, \ie, old application software and \AEDL\ files should, with minor
modifications, run with the new version as well.  However, some function names and features will
evolve during time, which means that outdated features may not be documented anymore.

@@

Here comes a summary of the most important changes in this version for users of earlier
versions of \GLOBES .

@@

\begin{itemize}
 \item
  User-defined systematics, which can be used to simulate reactor experiments \etc ; see \Sec~\ref{sec:userchi}
and~\ref{sec:rules}
 \item
  User-defined priors to include arbitrary external information in the $\chi^2$ before
marginalization over the oscillation parameters; see \Sec~\ref{sec:userdefined} 
\item
  Non-standard physics support; see \Chapt~\ref{chapt:nsphysics}
\item
  Beta beam fluxes available as built-in fluxes; see \Sec~\ref{sec:source}
\item
  Enhanced support for parallelization, such as Condor; see, \eg, page~\pageref{sec:condor}
\item
  Updated AEDL files; see \Tab~\ref{tab:experiments}
\item
 New \AEDL\ features, such as the support of lists as variables and an interpolation
routine; see \Sec~\ref{sec:advaedl}
\item
 Clean-up of inconsistencies, such as an overall (internal) normalization factor in the flux files;
see, \eg, page~\pageref{app:flux}
\item
  Faster probability engine, easier installation (internal changes)
\item
  Experimental feature: Alternative minimizer provided, which is usually faster than
the standard minimizer; see \Chapt~\ref{chapt:experimental}
\end{itemize}

@@

Most of the modifications should not require that old pieces of software be changed. 
However, the following changes are relevant:
\begin{itemize}
\item
 AEDL requires now that {\tt \$version} be used to define the minimum version number this AEDL
file is to be used with. With this requirement one can easily avoid that new AEDL
files with new features be used with old versions of \GLOBES\ which may not recognize these features.
\item
 Some of the earlier AEDL files have been updated, changed names, or have been removed. In addition, new files have been added. Although old AEDL files will run as usual for compatibility, they will not be
supported by the \GLOBES\ team anymore. You should make sure to keep these files when updating \GLOBES . 
\end{itemize}

\subsection*{Minor changes}

Here we document the most important changes which should not affect older software:
\begin{itemize}
\item
 Functions and constants renamed for consistency:
\begin{itemize}
\item
 {\tt glbChiTheta} $\rightarrow$ {\tt glbChiTheta13}
\item
 {\tt glbChiThetaDelta} $\rightarrow$ {\tt glbChiTheta13Delta}
\item
 {\tt glbChiDms} $\rightarrow$ {\tt glbChiDm21}
\item
 {\tt glbChiDm} $\rightarrow$ {\tt glbChiDm31}
\item
 {\tt GLB\_DM\_SOL} $\rightarrow$ {\tt GLB\_DM\_21}
\item
 {\tt GLB\_DM\_ATM} $\rightarrow$ {\tt GLB\_DM\_31}
\item
 {\tt glbSetStartingValues} $\rightarrow$ {\tt glbSetCentralValues}
\item
 {\tt glbGetStartingValues} $\rightarrow$ {\tt glbGetCentralValues}
\item
 {\tt glbGetProfileData} $\rightarrow$ {\tt glbGetProfileDataInExperiment}
\end{itemize}
\item
 Rate access changed; see \Sec~\ref{sec:event_rates}
\item
 Systematics concept changed, concept of error dimensions removed; {\tt @backgroundcenter} removed, central values for all systematics parameters
now zero; see \Sec~\ref{sec:rules}
\end{itemize}

### 2007-01-11 Documentation/appendix.tex
*** empty log message ***

\section*{\GLOBES\ and Condor}
\index{norm}{Condor|(}
\begin{quote}
  Condor is a specialized workload management system for
  compute-intensive jobs. Like other full-featured batch systems,
  Condor provides a job queuing mechanism, scheduling policy,
  priority scheme, resource monitoring, and resource management.
\end{quote}

@@

A common issue with \GLOBES\ is confusion about the proper units for
the input flux files for use in \AEDL\ experiment descriptions. Source of
the confusion is an undocumented factor 5.2 in \GLOBES\ versions older
than 3.0 the fluxes are multiplied with (see below). In Version 3.0 and 
higher, the alternative flux environment {\tt nuflux} is provided, 
which does not contain this factor. The following material is
based on the old environment {\tt flux}. For the use of {\tt nuflux},
replace the factor 5.20034 by unity.

@@

In understanding how one still can figure out what the correct units
are for each case, it is a good starting point to look at what
\GLOBES\ does with the input files. The cross section in the file is given as
differential cross section divided by energy $x=\sigma/E$, and the flux file
gives $f$. The differential number of events per GeV $n$ as computed in
\GLOBES\ without oscillation and efficiencies is given by
\begin{eqnarray}
n &=& 5.20034\times x\times E\times f\times \nonumber \\
&&\mathtt{@norm}\times\mathtt{@power}\times\mathtt{@stored\_muons}\times\mathtt{@time}\times\mathtt{\$target\_mass}\times(\mathtt{\$baseline})^{-2} \nonumber
\end{eqnarray}
Note that $5.20034$ is a undocumented fudge factor!

@@

\GLOBES\ assumes that the cross
section $x$ is given in $10^{-38}\,\mathrm{cm}^2$ and that all fluxes are
given at a distance of $1\,\mathrm{km}$. In addition, it assumes that
the number of target nuclei $\tau$ (or protons or whatever applies to the
given cross section) per unit target mass $m_u$ (which usually is $kt$)
 are properly accounted for.\footnote{Note that the cross sections which are delivered with
  \GLOBES\ always are per nucleon.}  Assuming that in the flux file
the data is given as number of neutrinos per unit area $A$ and
energy bin of width $\Delta E$ at a distance $L$ from the source, one
obtains
\begin{eqnarray}
\mathtt{@norm}=\frac{1}{5.20034}\left(\frac{\mathrm{GeV}}{\Delta
      E}\right)
\left(\frac{\mathrm{cm}^2}{A}\right)\left(\frac{L}{\mathrm{km}}\right)^2\left(\frac{\tau}{m_u}\right)\times10^{-38}\times\left(\frac{\mathcal{L}_u}{\mathcal{L}}\right)
\end{eqnarray}
where $\mathcal{L}$ absorbs all factors in the flux file related to
the integrated luminosity, and $\mathcal{L}_u$ is the unit chosen for
it.  The concept of integrated luminosity is
nicely described in the \GLOBES\ manual in \Sec~\ref{sec:source}.
A little example illustrates this concept:
The flux is given for $10^{21}\, \mathrm{pot}\,\mathrm{y}^{-1}$ of
$10\,\mathrm{GeV}$ protons, thus a good choice for the units $\mathcal{L}_u$
is $\mathrm{MW}\,\mathrm{y}^{-1}$, which means that
$\mathcal{L}/\mathcal{L}_u$ is given by (assuming a $10^7\,\mathrm{s}$
year)
\begin{equation}
\frac{\mathcal{L}}{\mathcal{L}_u}=\frac{10\,\mathrm{GeV}\,10^{21}\,\mathrm{pot}\,\mathrm{y}}{10^7\,\mathrm{s}}\times(\mathrm{MW}\,\mathrm{y}^{-1})^{-1}=0.160218\ldots
\end{equation}

>>>>

\section*{\GLOBES\ and Condor}
\label{sec:condor}
\index{norm}{Condor|(}
\begin{quote}
  Condor is a specialized workload management system for
  compute-intensive jobs. Like other full-featured batch systems,
  Condor provides a job queuing mechanism, scheduling policy,
  priority scheme, resource monitoring, and resource management.
\end{quote}

@@

A common issue with \GLOBES\ is confusion about the proper units for
the input flux files for use in \AEDL\ experiment descriptions. Source of
the confusion is an undocumented factor 5.2 in \GLOBES\ versions older
than 3.0 the fluxes are multiplied with (see below). In Version 3.0 and 
higher, the alternative flux environment {\tt nuflux} is provided, 
which does not contain this factor. The following material is
based on the old environment {\tt flux}. For the use of {\tt nuflux},
replace the factor 5.2 by unity.

@@

In understanding how one still can figure out what the correct units
are for each case, it is a good starting point to look at what
\GLOBES\ does with the input files. The cross section in the file is given as
differential cross section divided by energy $x=\sigma/E$, and the flux file
gives $f$. The differential number of events per GeV $n$ as computed in
\GLOBES\ without oscillation and efficiencies is given by
\begin{eqnarray}
n &=& 5.2\times x\times E\times f\times \nonumber \\
&&\mathtt{@norm}\times\mathtt{@power}\times\mathtt{@stored\_muons}\times\mathtt{@time}\times\mathtt{\$target\_mass}\times(\mathtt{\$baseline})^{-2} \nonumber
\end{eqnarray}
Note that $5.2$ is a undocumented fudge factor!

@@

\GLOBES\ assumes that the cross
section $x$ is given in $10^{-38}\,\mathrm{cm}^2$ and that all fluxes are
given at a distance of $1\,\mathrm{km}$. In addition, it assumes that
the number of target nuclei $\tau$ (or protons or whatever applies to the
given cross section) per unit target mass $m_u$ (which usually is $kt$)
 are properly accounted for.\footnote{Note that the cross sections which are delivered with
  \GLOBES\ always are per nucleon.}  Assuming that in the flux file
the data is given as number of neutrinos per unit area $A$ and
energy bin of width $\Delta E$ at a distance $L$ from the source, one
obtains
\begin{eqnarray}
\mathtt{@norm}=\frac{1}{5.2}\left(\frac{\mathrm{GeV}}{\Delta
      E}\right)
\left(\frac{\mathrm{cm}^2}{A}\right)\left(\frac{L}{\mathrm{km}}\right)^2\left(\frac{\tau}{m_u}\right)\times10^{-38}\times\left(\frac{\mathcal{L}_u}{\mathcal{L}}\right)
\end{eqnarray}
where $\mathcal{L}$ absorbs all factors in the flux file related to
the integrated luminosity, and $\mathcal{L}_u$ is the unit chosen for
it.  The concept of integrated luminosity is
nicely described in the \GLOBES\ manual in \Sec~\ref{sec:source}.
A little example illustrates this concept:
The flux is given for $10^{21}\, \mathrm{pot}\,\mathrm{y}^{-1}$ of
$10\,\mathrm{GeV}$ protons, thus a good choice for the units $\mathcal{L}_u$
is $\mathrm{MW}\,\mathrm{y}^{-1}$, which means that
$\mathcal{L}/\mathcal{L}_u$ is given by (assuming a $10^7\,\mathrm{s}$
year)
\begin{equation}
\frac{\mathcal{L}}{\mathcal{L}_u}=\frac{10\,\mathrm{GeV}\,10^{21}\,\mathrm{pot}\,\mathrm{y}}{10^7\,\mathrm{s}}\times(\mathrm{MW}\,\mathrm{y}^{-1})^{-1}=0.16\ldots
\end{equation}

\section*{Moving from {\tt flux} to {\tt nuflux}}

In order to change the older {\tt flux} environment to the
new {\tt nuflux} (\GLOBES\ 3.0 and higher), replace all user-defined fluxes, such as
\begin{quote}
{\tt flux(\#user)<}\\
{\tt \tb @flux\_file = "user\_file\_1.dat"\\
\tb @time = 2.0\\
\tb @power = 4.0\\
\tb @norm = 1e+8}\\
{\tt >}
\end{quote}
by
\begin{quote}
{\tt FF=5.1989} \\
\\
{\tt nuflux(\#user)<}\\
{\tt \tb @flux\_file = "user\_file\_1.dat"\\
\tb @time = 2.0\\
\tb @power = 4.0\\
\tb @norm = FF*1e+8}\\
{\tt >}
\end{quote}

This replacement is not necessary for neutrino factory built-in fluxes,
and built-in beta beams fluxes where not supported by earlier versions
of \GLOBES .

IS THAT CORRECT? MR: WHAT HAPPENS TO OLD BETA BEAM FILES [WW]?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2007-01-11 Documentation/part1.tex
*** empty log message ***

Another piece of information will be returned from the minimizers 
(\cf, \Chapt~\ref{chapt:correlations}) and transferred
into the {\tt glb\_params} structure is the number
of iterations used for the minimization, which is proportional to the
running time of the minimizer. In general, the user does not need to
access the elements in {\tt glb\_params} directly. A number of functions
is provided to handle these parameter structures:
\begin{function}
\GLBNS{AllocParams}
{\tt glb\_params glbAllocParams()} allocates the memory space
needed for a parameter vector and returns a pointer to it. All parameter values are
initially set to {\tt nan} (not a number).
\end{function}
\begin{function}
\GLBNS{AllocParams}
{\tt void glbFreeParams(glb\_params stale)} frees the memory
needed for a parameter vector {\tt stale} and sets the pointer to {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{DefineParams}
{\tt glb\_params glbDefineParams(glb\_params in, double theta12, double theta13,double theta23, double delta, double dm21, double dm31)} assigns
the complete set of oscillation parameters to the vector {\tt in}, which has
to be allocated before. The return value is the pointer to {\tt in} if 
the assignment was successful, and {\tt NULL} otherwise.
\end{function}
\begin{function}
 \GLBNS{CopyParams}
 {\tt glb\_params glbCopyParams(const glb\_params source, glb\_params dest)}
 copies the vector {\tt source} to the vector {\tt destination}. The return
 value is {\tt NULL} if the assignment was not successful.
\end{function}
\begin{function}
\GLBNS{PrintParams}
{\tt void glbPrintParams(FILE *stream, const glb\_params in)} prints the
parameters in {\tt in} to the file {\tt stream}. The oscillation
parameters, all density values, and the number of iterations are
printed as pretty output. Use {\tt stdout} for {\tt stream} if you want
to print to the screen.
\end{function}
In addition to these basic functions, there are functions to access
the individual parameters within the parameter vectors:
\begin{function}
\GLBNS{SetOscParams}
{\tt glb\_params glbSetOscParams(glb\_params in, double osc, int which)}
sets the oscillation parameter {\tt which} in the structure {\tt in}
to the value {\tt osc}. If the assignment was unsuccessful, the 
function returns {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{GetOscParams}
{\tt double glbGetOscParams(glb\_params in, int which)}
returns the value of the oscillation parameter {\tt which} in the 
structure {\tt in}.
\end{function}
In both of these functions, the parameter {\tt which} runs from
$0$ to $5$ (or the number of oscillation parameters-1), where the parameters in \GLOBES\ always have the order $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\deltacp$, $\sdm$, $\ldm$.
Alternatively to the number, the constants \GLBC{GLB\_THETA\_12}, \GLBC{GLB\_THETA\_13}, \GLBC{GLB\_THETA\_23}, \GLBC{GLB\_DELTA\_CP}, 
\GLBC{GLB\_DM\_SOL}, or \GLBC{GLB\_DM\_ATM} can be used.

@@

\section{Version control}
\label{sec:versioning}
\index{norm}{Version control}

@@

\begin{function}
\GLBNS{VersionOfExperiment} 
{\tt const char* glbVersionOfExperiment(int experiment)} returns
the version string of the experiment number {\tt experiment} (set by
{\tt \$version} in AEDL).
The version string is allocated within the experiment structure, which means
that it cannot be altered and must not be freed by the
user.
\end{function}

@@

Changing the systematics at running time can be useful to investigate
the impact factors affecting the measurement.
In \GLOBES , the systematics is defined rule-based, \ie, each rule
has its own systematics. 
In addition, \GLOBES\ supports dual systematics, \ie, \AEDL\ requires that it has to be
defined in each rule what ``Systematics on'' and ``Systematics off'' means.
In principle, these two sets correspond to two completely different systematics
implementations, and it is up to the \AEDL\ authors to define what that means.
From the point of view of the API, it is very simple to switch the systematics on and off, \ie,
to switch between the two systematics modes:
\begin{function}
\GLBNS{SwitchSystematics}
{\tt int glbSwitchSystematics(int exp, int rule, int on\_off)}
switches the systematics in experiment {\tt exp} and rule {\tt rule}
on ({\tt on\_off} is \GLBC{GLB\_ON}) or off ({\tt on\_off} is \GLBC{GLB\_OFF}). For the experiment or
rule index, one can also use \GLBC{GLB\_ALL}. 
\end{function}
One can also return the systematics state with
\begin{function}
\GLBNS{GetSysOnOffState}
{\tt int glbGetSysOnOffState(int exp, int rule)}
returns the systematics state in experiment {\tt exp} and rule {\tt rule}. 
\end{function}
In the example on page~\pageref{ex:barcharts}, the application of
{\tt glbSwitchSystematics} is demonstrated to show the impact of
systematics, correlations, and degeneracies.
Note that also the systematics function itself may be changed during running time,
as described in \Sec~\ref{sec:userchi}.

@@

\chapter{Experimental features}

>>>>

Another piece of information will be returned from the minimizers 
(\cf, \Chapt~\ref{chapt:correlations}) and transferred
into the {\tt glb\_params} structure is the number
of iterations used for the minimization, which is proportional to the
running time of the minimizer. In general, the user does not need to
access the elements in {\tt glb\_params} directly. A number of functions
is provided to handle these parameter structures:
\begin{function}
\GLBNS{AllocParams}
{\tt glb\_params glbAllocParams()} allocates the memory space
needed for a parameter vector and returns a pointer to it. All parameter values are
initially set to {\tt nan} (not a number).
\end{function}
\begin{function}
\GLBNS{AllocParams}
{\tt void glbFreeParams(glb\_params stale)} frees the memory
needed for a parameter vector {\tt stale} and sets the pointer to {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{DefineParams}
{\tt glb\_params glbDefineParams(glb\_params in, double theta12, double theta13,double theta23, double delta, double dm21, double dm31)} assigns
the complete set of oscillation parameters to the vector {\tt in}, which has
to be allocated before. The return value is the pointer to {\tt in} if 
the assignment was successful, and {\tt NULL} otherwise.
\end{function}
\begin{function}
 \GLBNS{CopyParams}
 {\tt glb\_params glbCopyParams(const glb\_params source, glb\_params dest)}
 copies the vector {\tt source} to the vector {\tt destination}. The return
 value is {\tt NULL} if the assignment was not successful.
\end{function}
\begin{function}
\GLBNS{PrintParams}
{\tt void glbPrintParams(FILE *stream, const glb\_params in)} prints the
parameters in {\tt in} to the file {\tt stream}. The oscillation
parameters, all density values, and the number of iterations are
printed as pretty output. Use {\tt stdout} for {\tt stream} if you want
to print to the screen.
\end{function}
In addition to these basic functions, there are functions to access
the individual parameters within the parameter vectors:
\begin{function}
\GLBNS{SetOscParams}
{\tt glb\_params glbSetOscParams(glb\_params in, double osc, int which)}
sets the oscillation parameter {\tt which} in the structure {\tt in}
to the value {\tt osc}. If the assignment was unsuccessful, the 
function returns {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{GetOscParams}
{\tt double glbGetOscParams(glb\_params in, int which)}
returns the value of the oscillation parameter {\tt which} in the 
structure {\tt in}.
\end{function}
In both of these functions, the parameter {\tt which} runs from
$0$ to $5$ (or the number of oscillation parameters-1), where the parameters in \GLOBES\ always have the order $\theta_{12}$, $\theta_{13}$, $\theta_{23}$, $\deltacp$, $\sdm$, $\ldm$.
Alternatively to the number, the constants \GLBC{GLB\_THETA\_12}, \GLBC{GLB\_THETA\_13}, \GLBC{GLB\_THETA\_23}, \GLBC{GLB\_DELTA\_CP}, 
\GLBC{GLB\_DM\_21}, or \GLBC{GLB\_DM\_31} can be used.

@@

\section{Version control and debugging}
\label{sec:versioning}
\index{norm}{Version control}

@@

\begin{function}
\GLBNS{VersionOfExperiment} 
{\tt const char* glbVersionOfExperiment(int experiment)} returns
the version string of the experiment number {\tt experiment} (set by
{\tt \$version} in AEDL).
The version string is allocated within the experiment structure, which means
that it cannot be altered and must not be freed by the
user.
\end{function}
%
A useful function to debug \GLOBES\ source code is 
\begin{function}
\GLBNS{SetVerbosityLevel}
{\tt int glbSetVerbosityLevel(int level)} sets the verbosity level
for \GLOBES\ messages.
\end{function}
The following verbosity levels are currently used:
\begin{description}
\item[0] Display no messages
\item[1] (Standard) Display error messages
\item[2] Display warnings
\item[3] Display file access history
\item[4] Display search paths
\end{description}
Note that always messages with the chosen verbosity level and lower
are displayed.

@@

Changing the systematics at running time can be useful to investigate
the impact factors affecting the measurement.
In \GLOBES , the systematics is defined rule-based, \ie, each rule
has its own systematics. 
In addition, \GLOBES\ supports dual systematics, \ie, \AEDL\ requires that it has to be
defined in each rule what ``Systematics on'' and ``Systematics off'' means.
In principle, these two sets correspond to two completely different systematics
implementations, and it is up to the \AEDL\ authors to define what that means.
From the point of view of the API, it is very simple to switch the systematics on and off, \ie,
to switch between the two systematics modes:
\begin{function}
\GLBNS{SwitchSystematics}
{\tt int glbSwitchSystematics(int exp, int rule, int on\_off)}
switches the systematics in experiment {\tt exp} and rule {\tt rule}
on ({\tt on\_off} is \GLBC{GLB\_ON}) or off ({\tt on\_off} is \GLBC{GLB\_OFF}). For the experiment or
rule index, one can also use \GLBC{GLB\_ALL}. 
\end{function}
One can also return the systematics state with
\begin{function}
\GLBNS{GetSysOnOffState}
{\tt int glbGetSysOnOffState(int exp, int rule)}
returns the systematics state in experiment {\tt exp} and rule {\tt rule}. 
\end{function}
In the example on page~\pageref{ex:barcharts}, the application of
{\tt glbSwitchSystematics} is demonstrated to show the impact of
systematics, correlations, and degeneracies.
Note that also the systematics function itself may be changed during running time
using \GLB{SetChiFunction}, as it is described in \Sec~\ref{sec:userchi}.

@@

\chapter{Experimental features}
\label{chapt:experimental}
